Models of lens candidates from Space Warps CFHTLS

### 2017-03-17 parts/morph.tex
ignacio changes

The third diagnostic is whether the lens is fairly isolated, or
whether there are other galaxies in the field that probably contribute
significantly to the lensing.  For this, we do not consider stars or
other clearly foregound objects.  Secondary lensing galaxies can be
marked by the volunteer alongside the spaghetti diagrams.  An example
can be seen as the grey dot and circle in the cutout with SW57 at the
top right of Figure~\ref{fig:splinput}.  Objects marked in this way
are modelled as point masses.  Other possible contributors to lensing
are galaxies or groups or that are not in the immediately vicinity of
the lensed images, yet massive enough to have an effect.  These are
allowed for by allowing a constant but adjustable external shear.

@@

\endinput

Let us first consider from SW05 (J143454.4+522850).
In SW05 there are four distinct lensed images, and the spaghetti
diagram proposes that they are a minimum nearest to the lensing
galaxy, a close minimum-saddle pair, and a minimum further away. In
Table~\ref{tab:models} we refer to such configurations as IQ for
inclined quad.

Figure~\figref{SW42} shows SW42.  The image morphology is similar to
SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky.

Proceeding to Figure~\figref{SW28}, we have one image close to the
galaxy and an arc further away, which is interpreted as a blend of
three images (a saddle point with two minima on either side).  We call
this a long-axis quad or LQ configuration.  It is an indication of a
mass distribution elongated along the arc-counterimage direction
(along EW in this case).

In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
an arc close the lensing galaxy and one image further away.  The arc
is interpreted three images (a minimum with two saddle points on
either side).  We call this a short-axis quad or SQ configuration.  It
is an indication of a mass distribution elongated perpendicular to the
arc-counterimage direction.

>>>>

The third diagnostic is whether the lens is fairly isolated, or
whether there are other galaxies in the field that probably contribute
significantly to the lensing.  For this, we do not consider stars or
other clearly foregound objects.  Secondary lensing galaxies can be
marked by the volunteer alongside the spaghetti diagrams.  An example
can be seen as the grey dot and circle in the cutout with SW57 at the
top right of Figure~\ref{fig:splinput}.  Objects marked in this way
are modelled as point masses.  Other possible contributors to lensing
are galaxies or groups or that are not in the immediately vicinity of
the lensed images, yet massive enough to have an effect.  These are
contributed for by allowing a constant but adjustable external shear.

@@
